\documentclass[a4paper]{exam}

\usepackage{amsmath,amssymb, amsthm}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titling}



% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS/MATH 113, SPRING 2025}{Pset 03: Inference}{\theauthor}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

% \printanswers %Uncomment this line

\title{Problem Set 03: Inference}
\author{Blingblong} % <=== replace with your student ID, e.g. xy012345
\date{CS/MATH 113 Discrete Mathematics\\Habib University\\Spring 2025}

% \qformat{\large\bf \thequestion.}
\qformat{{\large\bf \thequestion. \thequestiontitle}\hfill}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}
    \titledquestion{Basic rules of inference}
    Given that the following statements are true
    \begin{itemize}
        \item $p \implies q$
        \item $s \land \neg p \implies \neg r$
        \item $V \implies \neg q$
        \item $(t \lor s) \land (\neg t \lor \neg U)$
        \item $U \implies V$
        \item $U$
    \end{itemize}
    Show that $\neg r$ is true.
    \begin{solution}
        % Enter solution here.
    \end{solution}


    \titledquestion{It's Hero time!}
    Professor Paradox has been taken captive by Eon. In order to save him you need to find his Chrononavigator which he hid somewhere.
    Lucky for you, he left clues behind to find the Chrononavigator. By using the following clues deduce where the Chrononavigator is hidden.
    \begin{itemize}
        \item If Mr.Smoothy is next to a Burger Shack, then the Chrononavigator is in the Plumber's headquarters.
        \item If Mr.Smoothy is not next to a Burger Shack or the Chrononavigator is buried under Baumann's Store, then the tree in the front of Billion Tower is an elm and the tree in the back of Billion Tower is not an oak.
        \item If the Chrononavigator is in the Argistix Security office, then the tree in the back of Billion Tower is not an oak.
        \item If the Chrononavigator is not buried under Baumann's Store, then the tree in front of Billion Tower is not an elm.
        \item The Chrononavigator is not in the Plumber's headquarters.
    \end{itemize}

    \begin{solution}
    % Enter solution here

    \end{solution}

    \titledquestion{Elementary my dear Watson}
    Following is a quote by Sherlock Holmes from \textit{“A Study in Scarlet”} in which he solves a murder case.
    \begin{quote}
    ``And now we come to the great question as to the reason why. Robbery has not been the object of the murder, for nothing was taken. Was it politics, then, or was it a woman? That is the question which confronted me. I was inclined from the first to the latter supposition. Political assassins are only too glad to do their work and fly. This murder had, on the contrary, been done most deliberately, and the perpetrator has left his tracks all over the room, showing he had been there all the time.''
    \end{quote}
    After stating the above, Sherlock Holmes concludes: \textit{``It was a woman''}.

    Show the premises and logical inferences involved in deducing the conclusion.

    \begin{solution}
        % Enter solution here
    \end{solution}

    \titledquestion{Rules of inference for quantified}
    \begin{parts}
        \part Show that if $\forall x(P(x) \implies (Q(x) \land S(x)))$ and $\forall x(P(x) \land R(x))$ are true, then $\forall x(R(x) \land S(x))$ is true.
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part Show that if $\forall x(P(x) \lor Q(x))$, $\forall x(\neg Q(x) \lor S(x))$, $\forall x(R(x) \implies \neg S(x))$, and $\exists x\neg P(x)$ are true, then $\exists x\neg R(x)$ is true.
        \begin{solution}
            % Enter solution here
        \end{solution}


    \end{parts}
    
    % 

    
      
\end{questions}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
